\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Weekly Bib Report 1}
\author{Alok Macharla }
\date{February 2021}

\begin{document}
\maketitle

\section{Source 1}
This source talks about the impact of Twitter's decision to ban former President Donald Trump from the social media site. The decision resulted in harsh criticisms from Trump and other right wing supporters as they claimed Twitter's actions were an infringement of the 1st amendment. On the other hand, Twitter's bold decision sparked a chain reaction which saw the President being banned from numerous popular social media sites such as Facebook. These unprecedented bans effective silenced one of the most powerful and outspoken world leaders overnight, and  illustrates the significant power that mobile applications now wield in society. As the development of mobile applications continue to progress, and more and more people gain access to mobile phones, the ability of mobile applications to impact society has grown alarmingly
Article: \cite{edsgcl.64787209220210109}

\section{Source 2}
This source refers to the recent controversial actions of the popular mobile investing application Robinhood. As a result of multiple contributing factors, Robinhood enabled amateur investors to flood the stock market and inflate the price of GameStop a video game retailer to record breaking levels in order to cause large investment funds to loose billions of dollars. The big take way from this sources is the ability of social media and mobile applications to have significant lasting impact on our society and more recently the largest institutions in our country, like the financial institution. The power of these seemingly harmless social media sites are displayed when combined with mobile apps, as social media has the power to unite and connect people of many different background while mobile apps like Robinhood enable these unified forces to create a lasting impact. 
Article: \cite{edsgcl.64530890420200101}

\bibliographystyle{plain}
\bibliography{sources}
\end{document}
